%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Kartabya Krishna} \\ \vspace{1pt}
    Manipal, Karnataka \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-7000716360 ~ \href{mailto:kartabyakrishna@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{KartabyaKrishna@gmail.com}} ~ 
   \href{https://linkedin.com/in/KartabyaKrishna}{\raisebox{-0.2\height}\faLinkedin\ \underline{/KartabyaKrishna}}  ~
    \href{https://github.com/KartabyaKrishna}{\raisebox{-0.2\height}\faGithub\ \underline{/KartabyaKrishna}} ~

    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Manipal Institue Of Technology}{Oct. 2021 -- Present}
      {Bachelor of Technology in Data Science Engineering (Honours) • Grade:\textbf{9.01}}{Manipal, Karnataka}
      \resumeSubheading
      {Aadarsh Vikas Vidyalaya}{Apr. 2018 -- Apr. 2020}
      {12th Standard • CBSE • Grade:\textbf{81.4\%} }{Patna, Bihar}
      \resumeSubheading
      {St. Joseph's High School}{May 2007 -- Mar. 2018}
      {10th Standard • CBSE • Grade:\textbf{91.5\%} }{Patna, Bihar}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Data Analysis
                \item Algorithms Analysis
                \item Database Management
                \item Machine Learning
                \item Deep Learning
                \item Artificial Intelligence
                \item Big Data Analysis
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
    {\textbf{Landslide Detection (Research Project)}}{July 2023 -- Present}
    \resumeItemListStart
        \resumeItem{\textbf{Algorithms}{: U-Net, TransUNet, DeepLab}}
        \resumeItem{\textbf{Languages / Libraries}{: Python, TensorFlow, Keras, OpenCV}}
        \resumeItem{Working on a research project focused on landslide detection.}
        \resumeItem{Incorporating digital elevation model data and masks using concatenation techniques to improve accuracy.}
        \resumeItem{Achieved an accuracy of 97\% and a Mean Intersection over Union (mIOU) of 0.66.}
        \resumeItem{Collaborating with a professor to develop this project, aiming to contribute to a research paper.}
        \resumeItem{Implemented U-Net and currently working on TransUNet and DeepLab networks for further improvement in segmentation accuracy.}
    \resumeItemListEnd
\vspace{-15pt}    
\resumeProjectHeading
    {\textbf{COVID-19 Lesion Detection}}{June 2023}
    \resumeItemListStart
        \resumeItem{\textbf{Algorithms}{: U-Net, PSPNet}}
        \resumeItem{\textbf{Languages / Libraries}{: Python, TensorFlow, Keras, OpenCV, Gradio}}
        \resumeItem{Developed a robust COVID-19 Lesion Detection system using deep learning techniques.}
        \resumeItem{Utilized state-of-the-art neural network architectures like U-Net and PSPNet for image segmentation.}
        \resumeItem{Achieved an outstanding accuracy of 98\% in detecting and segmenting lung lesions indicative of COVID-19 on medical images, through rigorous hyperparameter tuning and optimization.}
        \resumeItem{Implemented the solution with TensorFlow and Keras for deep learning and utilized OpenCV for image processing.}
        \resumeItem{Created a user-friendly GUI using Gradio to allow easy interaction with the model, enhancing accessibility for healthcare professionals.}
        \resumeItem{Generated precise masks representing the lesions on individuals' lungs, contributing to the early diagnosis of COVID-19 cases.}
    \resumeItemListEnd
\vspace{-15pt}
\resumeProjectHeading
    {\textbf{Online Retail Management System}}{April 2023}
    \resumeItemListStart
        \resumeItem{\textbf{Technologies}{: SQL, Database Management, Command Prompt UI}}
        \resumeItem{Developed an Online Retail Management System with an admin-level database management component.}
        \resumeItem{Designed a command prompt-based user interface for easy interaction.}
        \resumeItem{Utilized SQL for database operations, including creating bills and analyzing sales and stock data.}
        \resumeItem{Implemented various SQL queries, functions, procedures, and triggers for database management, enhancing skills for the Database System Labs course.}
    \resumeItemListEnd
\vspace{-15pt}
\resumeProjectHeading
    {\textbf{Sudoku Solver}}{September 2022}
    \resumeItemListStart
        \resumeItem{\textbf{Technologies}{: C++, Backtracking Algorithm, Vector}}
        \resumeItem{Developed a Sudoku solver program in C++ that could solve Sudoku puzzles.}
        \resumeItem{Implemented the backtracking algorithm to find a solution for Sudoku puzzles.}
        \resumeItem{Utilized data structures like vectors to efficiently handle and manipulate Sudoku grids.}
        \resumeItem{Enhanced understanding of data structures, which was beneficial for the Data Structures Lab course.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-15pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Data Analysis}{: Pandas, NumPy, Matplotlib, Seaborn} \\
     \textbf{Languages}{:  Python (including TensorFlow, OpenCV), C++, Java, SQL} \\
     \textbf{Developer Tools}{: GitHub, Visual Studio Code (VS Code)} \\
     \textbf{Web Technologies}{: HTML, CSS, JavaScript} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\section{Achievements}
\resumeSubHeadingListStart
\resumeSubheading
{Awarded Achiever's Scholarship of Rs. 97,000}{October 2023}{Manipal Institute of Technology}{}
\resumeItemListStart
\resumeItem{Awarded an Achiever's Scholarship of Rs. 97,000 for outstanding academic performance in 2022-23.}
\resumeItem{Achieved 2nd rank in iVth Semester , demonstrating exceptional performance and dedication.}
\resumeItem{Successfully secured the opportunity to pursue a Bachelor of Technology (B.Tech) Honours degree.}
\resumeItem{Highlighted strong academic prowess and commitment to excellence.}
\resumeItemListEnd

\resumeSubheading
  {SIH Nomination for AgriHealthGuru}{September 2023}{Manipal Institute of Technology}{}
  \resumeItemListStart
    \resumeItem{Nominated as a team member for the Smart India Hackathon (SIH) for the project "AgriHealthGuru."}
    \resumeItem{Developed an app for plant health disease detection as part of the team "SPAM.ik."}
    \resumeItem{Led the deep learning model generation and documentation efforts for the project.}
  \resumeItemListEnd
  
\resumeSubheading
  {NTSE Stage 1 Qualifier}{May 2019}{St. Joseph's High School, Patna, Bihar}{}
  \resumeItemListStart
    \resumeItem{Qualified the National Talent Search Examination (NTSE) Stage 1, showcasing excellence in academics during high school.}
  \resumeItemListEnd



% Add more achievements here as needed

\resumeSubHeadingListEnd


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}

\resumeSubHeadingListStart

\resumeSubheading{The Data Alchemists}{August 2023 -- Present}{Board Member, Graphics/Social Media Head and Admin/Maintainer on \href{https://github.com/The-Data-Alchemists-Manipal}{GitHub}}{MIT, Manipal}

\resumeItemListStart

\resumeItem{Contributing as a board member to the strategic direction of The Data Alchemists, a Data-Science Student Club.}

\resumeItem{Manage graphics and social media content creation to enhance the organization's online presence and engagement.}

\resumeItem{Collaborate with the board to develop and execute initiatives related to data science and analytics.}

\resumeItem{Serve as admin and maintainer on  \href{https://github.com/The-Data-Alchemists-Manipal}{The Data Alchemists Organization} to manage repositories.}

\resumeItemListEnd

\resumeSubHeadingListEnd


\end{document}
